---
title: "Assignment 4_ggplot2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Chapter 1 of ggplot2

Explanatory vs. Exploratory
Graphics: distint layers of grammatical elements 
```{r cars}
install.packages("ggplot2")
library(ggplot2)

```

## Creating dataframes: planets_df

You can also embed plots, for example:

```{r pressure, echo=FALSE}
# Definition of vectors
name <- c("Mercury", "Venus", "Earth", "Mars", "Jupiter", "Saturn", "Uranus", "Neptune")
type <- c("Terrestrial planet", "Terrestrial planet", "Terrestrial planet", 
          "Terrestrial planet", "Gas giant", "Gas giant", "Gas giant", "Gas giant")
diameter <- c(0.382, 0.949, 1, 0.532, 11.209, 9.449, 4.007, 3.883)
rotation <- c(58.64, -243.02, 1, 1.03, 0.41, 0.43, -0.72, 0.67)
rings <- c(FALSE, FALSE, FALSE, FALSE, TRUE, TRUE, TRUE, TRUE)

# Create a data frame from the vectors
planets_df <-data.frame(name, type, diameter, rotation, rings)
```

Plotting rotation(x) against diameter (y)  with color = type  
```{r}
ggplot(planets_df, aes(x = rotation, y = diameter, color = type)) +
  geom_point()
```
Recycling ggplots with modifications in the geomplot()
```{r}
dia_planets <- ggplot(planets_df, aes(x = rotation, y = diameter))
dia_planets + geom_point(aes(color = rings))
```
Creating a new dataframe for chapter 2 
```{r}
# Definition of vectors
pencil.length <- c(10, 22, 14, 15, 77, 20)
pencil.width <- c(13, 52, 16, 45, 71, 24)
eraser.length <- c(1, 2, 3,1, 1, 1)
eraser.width <- c(1, 3, 2,2, 1, 1)
pencil_color <- c("red", "blue", "pink")

# Create a data frame from the vectors
the_pencil <-data.frame(pencil.length, pencil.width, eraser.length, eraser.width, pencil_color)
```
Creating the_pencil_tidy
```{r}
# Load the tidyr package
library(tidyr)

# creating th_pencil_wide
the_pencil.tidy <- the_pencil %>%
  gather(key, Value, -pencil_color) %>%
  separate(key, c("Part", "Measure"), "\\.")
```
# Map mpg onto x, qsec onto y and factor(cyl) onto col (3 aesthetics):
ggplot(mtcars, aes(x = mpg, y = qsec, col = factor(cyl))) +
  geom_point()

# Add mapping: factor(am) onto shape (now 4 aesthetics):
ggplot(mtcars, aes(x = mpg, y = qsec, col = factor(cyl), shape = factor(am))) +
  geom_point()

# Add mapping: (hp/wt) onto size (now 5 aesthetics):
ggplot(mtcars, aes(x = mpg, y = qsec, col = factor(cyl), shape = factor(am), size = (hp/wt))) +
  geom_point()
  
  
  
  
  
  # Hollow circles - an improvement
ggplot(mtcars, aes(x = wt, y = mpg, color = cyl)) +
  geom_point(size = 4, shape = 1)

# Add transparency - very nice
ggplot(mtcars, aes(x = wt, y = mpg, color = cyl)) +
  geom_point(size = 4, alpha = 0.6)
  
  
  
  # Adjust for overplotting
ggplot(diamonds, aes(x = carat, y = price, color = clarity)) +
  geom_point(alpha = 0.5)
  
  
  # 1 - Make a univariate histogram
ggplot(mtcars, aes(mpg)) +
  geom_histogram()
  
  # Draw a bar plot of cyl, filled according to am
ggplot(mtcars, aes(x = cyl, fill = am)) +
  geom_bar()